D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Clarify what we are asking of the standard
Namely, a small non-normative change.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Add D3692P1 item to history section
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code.
	As a consequence, we are not asking for any normative changes
	to the standard.

@@

This paper is a condensation of P3064R2 (``How to Avoid OOTA Without
Really Trying'')~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
which was criticized as being overly long.
It also adds citations and clarifications.

>>>>

	It follows that enforcing OOTA avoidance requires no special
	action from implementations and no changes to user code.
	As a consequence, we are asking for only for a small non-normative
	change to the standard.

@@

\begin{itemize}
\item	D3692R1 adds contact information, defines ``preserved
	dependencies'' that are a subset of syntactic and a superset of
	semantic dependencies, and makes numerous changes in the name
	of wordsmithing and clarification.
\item	This paper is a condensation of P3064R2 (``How to Avoid OOTA
	Without Really
	Trying'')~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
	which was criticized as being overly long.
	It also adds citations and clarifications.
\end{itemize}
